Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-08 paper.tex
energy

\section{\uppercase{State of Art}}
\label{sec:state}
Our solutions is based on GPU virtualization and sharing resources in order
to reach a fair balance between supply and demand.
Several attempts of achieving what we are pursing have been
made, but none of them are so ambitious as our project. On
the one hand the work done in~\cite{younge2013enabling} allows the VM managed
by the hypervisor Xen to access the GPUs in the physical
node. With the implied limitations of restricting the nodes not
to use more GPUs than the hosted in the machine and not
to share idle GPUs to other machines, several solutions have been presented.
The solution presented by the project gVirtus~\cite{giunta2010gpgpu} does virtualize GPUs and make
them accessible for any VM in the cluster. However, this kind
of virtualization strongly depends on the hypervisor used, so
does its performance. Another similar solution is presented in~\cite{diab2013dynamic} by the name of gCloud. 
This one continues without being integrated in a Cloud Computing Manager, though its main
drawback is that the code of the applications must be modified
in order to be run in their virtual-GPU environment. A runtime component to provide abstraction
and sharing of GPUs is presented in~\cite{becchi2012virtual}, which allows scheduling policies 
to isolate and share GPUs in a cluster for a set of applications. Our proposal uses a different 
approach employing virtual machines and a cloud computing environment to allow to share GPUs in a flexible way.
On the other hand, the work exposed in~\cite{jungpgpu} is more mature, however,
it is only focussed on compute intensive HPC applications. 
The main idea of our proposal goes further and apart from
bringing solutions for all kind of HPC applications, it is aimed
to boost the cluster flexibility in the use of GPUs.

@@

For this study, carried out in June 2015, we worked in the AWS availability zone US EAST (N. VIRGINIA). 
So, at this moment the instances used had the features presented in the Table~\ref{table:awsInstances}.

@@

The IPERF\footnote{\url{http://iperf.fr/}} tool has been executed between the instances showed in 
the Table~\ref{table:iperf} in order to know the real bandwidth.
Therefore, we can assure that the nomenclature ``High'' used in the 
network column correspond to a 1~Gb interconnection and the 10~Gb has 
a real bandwidth of 7.5~Gb/s.
Moreover, it looks like the instances equipped with a ``High'' interconnection 
are software-limited up to 1~Gb/s due to the theoretical and real bandwith 
match perfectly. The gap between real and theorical can be observed with 
the 10~Gb interconnection which reaches up to 7.5~Gb/s.

@@

@@

>>>>

\section{\uppercase{State of Art}}
\label{sec:state}
Our solutions
is based on GPU virtualization and sharing resources in order
to reach a fair balance between supply and demand.
Several attempts of achieving what we are pursing have been
made, but none of them are so ambitious as our project. On
the one hand the work done in~\cite{younge2013enabling} allows the VM managed
by the hypervisor Xen to access the GPUs in the physical
node. With the implied limitations of restricting the nodes not
to use more GPUs than the hosted in the machine and not
to share idle GPUs to other machines. The solution presented
by the project gVirtus~\cite{giunta2010gpgpu} does virtualize GPUs and make
them accessible for any VM in the cluster. However, this kind
of virtualization strongly depends on the hypervisor used, so
does its performance. Another similar solution is presented in~\cite{diab2013dynamic} by the name of gCloud. This one continues without being
integrated in a Cloud Computing Manager, though its main
drawback is that the code of the applications must be modified
in order to be run in their virtual-GPU environment. On the
other hand, the work exposed in~\cite{jungpgpu} is more mature, however,
it is only focussed on compute intensive HPC applications.
The main idea of our proposal goes further and apart from
bringing solutions for all kind of HPC applications, it is aimed
to boost the cluster flexibility in the use of GPUs.

@@

For this study, carried out in June 2015, we worked in the AWS availability zone US EAST (N. VIRGINIA). 
So, at that moment the instances used had the features presented in the Table~\ref{table:awsInstances}.

@@

The IPERF tool has been executed between the instances showed in 
the Table~\ref{table:iperf} in order to know the real bandwidth.
Therefore, we can assure that the nomenclature ``High'' used in the 
network column correspond to a 1~Gb interconnection and the 10~Gb has 
a real bandwidth of 7.5~Gb/s.
Moreover, it looks like the instances equipped with a ``High'' interconnection 
are software-limited up to 1~Gb/s due to the theoretical and real bandwith 
match perfectly. The gap between real and theorical can be observed with 
the 10~Gb interconnection which reaches up to 7.5~Gb/s.

@@

All the instances deployed operate the RHEL 7.1 64 bit system and the version 6.5 of CUDA.

@@

Other interesting approach would be to make the system energy-aware. 
Provided that a GPU could throw power information, a similar study based on the energy consumption could be done.
